\textbf{Discrete Bulk Reconstruction Problem} \\ \large Compiled Research

### 2025-03-07 paper.tex
added text

\begin{abstract}
    This is example abstract. 
\end{abstract}

@@

\section{Introduction}
    Intro provides background info, motivation, and objective of research. Explain why problem is important and summarize prior work

\section{Methodology}
Describe your approach, methods, and any theoretical background required. If you include equations, use:

\section*{Background}

\subsection*{AdS (Anti-de Sitter)}
\begin{itemize}
    \item Higher-dimensional \textbf{bulk} space
    \item \textbf{Bulk}: AdS space
    \item \textbf{Surface}: Geometric object within AdS space
    \item \textbf{Minimal area}: Surface that spans the boundary subregion and has the smallest possible area \textit{(RT surface in AdS/CFT)}
    \item The bulk is very hard to calculate directly because of quantum gravity, therefore perform calculations on CFT.
\end{itemize}

\subsection*{CFT (Conformal Field Theory)}
\begin{itemize}
    \item \textbf{Boundary} $\Rightarrow$ CFT
    \item Lower-dimensional space that forms "edge" or "boundary" of AdS bulk
    \item Non-gravitational theory that lives on the boundary of the AdS spacetime
    \item Information of boundary is encoded in the bulk
\end{itemize}

>>>>

%%%%%%%%%%%%%%% ABSTRACT %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
    The \textbf{Discrete Bulk Reconstruction Problem (DBRP)} models the entanglement structure of quantum systems using discrete graphs. It is rooted in the Anti-de Sitter / Conformal Field Theory (AdS/CFT) correspondence, which connects a gravitational theory in AdS space (the bulk) to its quantum field theory on its boundary (the CFT).
    While this describes a universe different from our own, it offers valuable insights into quantum gravity and spacetime emergence. 
    \\
    \indent Instead of using traditional approaches that rely on continous AdS space, DBRP models the bulk as a graph, where nodes correspond to regions of space and edge weights encode entanglement connectivity.
    In this framework, geodesics in AdS are approximated by min-cuts in the graph, and the Ryu-Takayanagi (RT) formula determines minimal surfaces in the bulk, allowing for bulk geometry reconstruction from boundary entanglement.
    \\
   \indent DBRP leverages tensory networks and holography to provide a discrete approach to understanding spacetime, quantum entanglement, and information flow.
    DBRP could provide profound insight in quantum gravity, improved quantum error correction, and practical quantum computing applications.
\end{abstract}

@@

%%%%%%%%%%%%%% INTRO %%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
    \hspace{0.5cm} DBRP aims to reconstruct spacetime (the bulk) from the entanglement structure of quantum systems. This structure is defined by the collection of entanglement entropies of its subsystems, which quantify how much information a given region of the system contains. More precisely, entanglement entropy measures how strongly a subsystem is correlated with the rest of the system.
    \\
    \indent A key motivation for DBRP comes from the AdS/CFT correspondence, first proposed by Juan Maldacena in 1997. This duality suggests that a (d + 1)-dimensional anti-de Sitter (AdS) space, which includes quantum gravity, is fully encoded by a d-dimensional conformal field theory (CFT) on its boundary. Because the CFT is non-gravitational, computations are easier, making this framework a powerful tool for understanding quantum gravity.
    \\
    \indent By leveraging insights from AdS/CFT, DBRP offers a discrete, graph-based approach to bulk reconstruction, which allows for a new perspective on how spacetime emerges from entanglement, with potential applications in both holography and quantum information theory.

\section{Explanation of "Universe"}
    \subsection*{AdS (Anti-de Sitter) Space $\Rightarrow$ The Bulk}
    \begin{itemize}
        \item The \textbf{bulk} represents a higher-dimensional space in the AdS/CFT framework.  
        \item A \textbf{surface} is a geometric object within AdS space that plays a crucial role in holography.  
        \item The \textbf{minimal area} surface, also known as the RT surface in AdS/CFT, spans the boundary subregion and has the smallest possible area.  
        \item Since direct calculations in the bulk are challenging due to quantum gravity, computations are instead performed on the CFT boundary.  
    \end{itemize}

    \subsection*{CFT (Conformal Field Theory) Space $\Rightarrow$ The Boundary}
    \begin{itemize}
        \item The \textbf{Boundary} represents a lower-dimensional space the forms "edge" or "boundary" of AdS bulk.
        \item \textbf{Non-gravitational} theory that lives on the boundary of the AdS spacetime.
        \item The information of boundary is encoded in the bulk.
    \end{itemize}
